The Importance of Affective States in Privacy Calculus

### 2021-05-01 submission.tex
Findings for Ad Tracking added

%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

>>>>

\subsection{Ad Tracking}
A strong relationship exists such that \emph{the better an individual feels when
they delete cookies, the more frequently they delete them}. This was determined
by obtaining the gamma correlation value of magnitude .821 (p<.01,**) between
ordinal values for ``How often do you delete cookies on the device you most
regularly use for browsing?'' and ``How do you feel when you delete cookies?''.
Despite the strength of the relationship, the Chi-Square p-value of .178
indicates that the null hypothesis cannot be ruled out.

\subsection{Privacy and Social Media}

\begin{figure}[H]
    \includegraphics[width=0.5\textwidth]{univariate social media practices}
    \caption{Respondents' actual privacy practices regarding on social media.
	Only respondents who indicated concern about social media privacy were
	asked to answer this question.}
    \label{Univariate Distribution Respondent Concerns}
\end{figure}
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}
